
\chapter{Introduction}
\label{chapter:intro}

This chapter gives an introduction to the

\section{Motivation}

- A few words on:
a) Why agile software development is being used in large organizations
b) Is the application of agile in some way difficult

- Miksi aiheena kiinnostava?

As the competition in software industry is growing companies are constantly
looking to improve their effectiveness. Agile methods are claimed to increase
productivity and quality \cite{Livermore2008}, which makes them attractive
for companies pursuing better performance.

- Miksi tämä case on kiinnostava?

- Motivation of the need of a literature review


\section{Objective and scope}

- A case study was set to be undertaken to contribute for more research on the topic

- Research questions

\begin{itemize}
  \item Why was the transformation initiated?
  \item How did the transformation proceed?
  \item What successes and challenges were encountered in the transformation
        process?
  \item Was the transformation seen as successful by the interviewees?
  \item How do performance measures compare before and after the transformation?
  \item How does the Ericsson LMF transformation compare to existing literature?
\end{itemize}

- Scope of the work.
What is left out?
What kind of questions are intended not to be answered?


\section{Structure of the thesis}

You should use transition in your text, meaning that you should help
the reader follow the thesis outline. Here, you tell what will be in
each chapter of your thesis. 

